\chapter{Applications and perspectives}
\addcontentsline{toc}{chapter}{Applications and perspectives}
\markboth{Applications and perspectives}{Applications and perspectives}
\label{chap:applications}
%\minitoc
\section{Applications}

Immediate applications of the similarity model developed in this work include:

\begin{enumerate}
    \item \textbf{Automated Design Optimization}:
    \begin{itemize}
        \item Leveraging the similarity model to suggest design improvements based on high-performing similar designs.
        \item Developing generative models that can propose new designs based on similarity-driven interpolation between existing successful designs.
    \end{itemize}

    \item \textbf{Integration with CAD Software}:
    \begin{itemize}
        \item Embedding the similarity model directly into CAD software for real-time suggestions during the design process.
        \item Creating plugins that allow for similarity-based search and retrieval directly within popular CAD environments.
        \item Embedding the model into D3S Costing Platform.
    \end{itemize}
\end{enumerate}

\section{Future Perspectives}
\label{sec:future-perspectives}

The work presented here opens up several avenues for future research and development:

\begin{enumerate}
    \item \textbf{Multi-modal Similarity Models}: 
    \begin{itemize}
        \item Integrating geometric data with textual descriptions, functional specifications, or material properties to create more comprehensive similarity metrics.
        \item Exploring the use of large language models to bridge the gap between natural language queries and geometric design features. \cite{liuOpenShapeScaling3D2023} uses CLIP to distill 2D and text representations knowledge to the 3D modality, but more recent papers like \cite{qiShapeLLMUniversal3D2024} use GPT 4 to chat with 3D models.
    \end{itemize}


    \item \textbf{Labeling tool for Active Learning}:
    \begin{itemize}
        \item Implementing active learning strategies to intelligently select new triplets for labeling, maximizing the information gain from human input.
    \end{itemize}


\end{enumerate}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "isae-report-template"
%%% End: 
